Thank you, Rachel, for always believing in me and wanting me to be happy. I couldn't have done this without you by my side or felt 1/10$^{th}$ as fulfilled. You have given me more patience than I deserve and supported me like no one else.

Clara, my little `science kid' and `pteranadon', thank you for being my sunrise in the morning and light at the end of the tunnel of a long day. You couldn't make me happier or more proud.

Thanks, Mom and Dad, for your love that is too big for words... or at least past the last star.

Jenna, Janelle, Jaron, Ed, and Eric; thanks for loving me, supporting me, and knowing me better than I know myself. Also, thank you, Janelle, for being so awesome at what you do that your boss thought it worthwhile to take a look at your brother for a traineeship!

Di and Dave, I don't know how I could have done this without your help. I really don't. Thank you.

Nora, Jed, Romeo, and Stella; thanks for enriching my life and being such fantastic partners in raising a family here in Madison.

Thank you Prof. Beebe for your exceptionally open mind, welcoming nature, and for taking a chance on a kid who decided car manufacturing just wasn't for him. I will always value your keen vision and subtle leadership.

Josh Posner, I am so lucky to count you among my friends. Thank you for your help.

Thank you, Prof. Williams, for being so helpful in my transition to Madison.

Thank you Prof. Murphy for your challenging questions, genuine encouragement, and willingness to help others.

Thank you Beebe Lab'ers. You make work not feel like work at all. I've had more laughs, deep discussions, and ridiculously good pot-lucks than I could have ever hoped for. Edmond, thanks for always seeing the bright side and being there for help when things just weren't working. Scott, we'll always have the Netherlands. Lindsey, Edmond, Ben, Mara, and Rachel; thanks for always having cells on hand. Keil, thanks for being the king of random knowledge from cooking and sailing to circuits and pathways. Erwin, thanks for all the mind bending brain-storming sessions that earned us the name Jerwin. `The Only, The Only' (no typo), thanks for teaching me flip-turns and for bringing your dreamer-enthusiasm absolutely every day... righteous. 

Thanks to the past Beebe Lab'ers: Amy, for the straight story; Vinay, for your realism; Bobby, for your enthusiasm and tandoori chicken; Moga, for Moga; Pooch for being able to fix anything; Megan, for putting up with me; Jongil, for your friendship; Mara, for your hilarious and sunny perspective on nearly all matters; and Ivar, for showing me the ropes and always having the time and incredible patience to answer `just one more question'.



